{\sc Kalashnikov}: Fully Automatic Loop Free Program Synthesis by Bounded Model Checking

### 2013-10-04 paper/paper.tex
Changed abstract

\abstract
We present a method for synthesizing loop free programs using a combination of
bounded model checking and explicit enumeration.  The user provides a specification
in plain C and is not required to interact further with the synthesis processs.
In particular the user need not tell the synthesizer which program components to
use.

We demonstrate the effectiveness of our method by synthesizing several tricky
bitvector programs and a selection of floating point programs.

>>>>

\begin{abstract}
We present a method for synthesizing loop-free programs, using a combination of
bounded model checking and explicit state model checking.  The user provides a
specification in plain C, after which the synthesis process is fully automatic.

We demonstrate the effectiveness of our method by synthesizing several subtle
programs acting on machine integers, and a selection of floating point programs.
\end{abstract}
